Distributional Trees and Forests

### 2017-06-26 pkg/disttree/inst/useR2017/slides.Rnw
changed 'col' and 'lwd' in density plot
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1493 255f4249-2263-4417-b1ea-8498779e27a7

    grid.lines(x = xd, y = yd, default.units = "native", 
               gp = gpar(col = col))
    grid.xaxis()
    grid.yaxis()
    grid.rect(gp = gpar(fill = "transparent"))
    upViewport(2)
  }
  return(rval)
}

@@

plot(tree, tnex = 1.4, drop = TRUE,
     terminal_panel = node_density(horizontal = TRUE, col = pal["forest"], lwd = 5),
     tp_args = list(fill = paltrees[c(1, 3)]), 
     ip_args = list(fill = paltrees[c(2, 3)]))
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.5cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.74\linewidth}
<<plottree_dens_v, fig=TRUE, echo=FALSE>>=
plot(tree, tnex = 1.4, drop = TRUE,
     terminal_panel = node_density(horizontal = FALSE),
     tp_args = list(fill = paltrees[c(1, 3)]), 
     ip_args = list(fill = paltrees[c(2, 3)]))
@
\end{center}
\end{frame}
%\begin{frame}
%\frametitle{Fitting a Tree}
%\center
%\vspace*{-1cm}
%\setkeys{Gin}{width=0.8\linewidth}
%\includegraphics{tree_box}
%\end{frame}

>>>>

    grid.lines(x = xd, y = yd, default.units = "native", 
               gp = gpar(col = col, lwd = lwd))
    grid.xaxis()
    grid.yaxis()
    grid.rect(gp = gpar(fill = "transparent"))
    upViewport(2)
  }
  return(rval)
}

@@

plot(tree, tnex = 1.4, drop = TRUE,
     terminal_panel = node_density(horizontal = TRUE, col = pal["forest"], lwd = 2),
     tp_args = list(fill = paltrees[c(1, 3)]), 
     ip_args = list(fill = paltrees[c(2, 3)]))
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.5cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.74\linewidth}
<<plottree_dens_v, fig=TRUE, echo=FALSE>>=
plot(tree, tnex = 1.4, drop = TRUE,
     terminal_panel = node_density(horizontal = FALSE, col = pal["forest"], lwd = 2),
     tp_args = list(fill = paltrees[c(1, 3)]), 
     ip_args = list(fill = paltrees[c(2, 3)]))
@
\end{center}
\end{frame}
%\begin{frame}
%\frametitle{Fitting a Tree}
%\center
%\vspace*{-1cm}
%\setkeys{Gin}{width=0.8\linewidth}
%\includegraphics{tree_box}
%\end{frame}
